Attrition in Massive Open Online Courses: Inequalities, Dropout Reasons, and Psychological Factors

### 2014-10-30 paper_v1.Rnw
pred plot correction for final sub

<<s1coefs, echo=FALSE, fig.env='figure*', fig.pos='ht', fig.height=6, fig.width=10, fig.cap='Coefficients of predictors (binary, except for normalized age) from logistic mixed-effects model predicting persistence and performance milestones (prop. videos watched, prop. assessments completed, and grade percentile). The baseline group were male learners in North America of average age who had not earned a bachelor\'s degree, without prior experience in the topic or other MOOCs, not intending to complete the course, and prepared to spend under two hours per week on it. An estimate of -20 indicates a 20\\% points lower probability of achieving a milestone.'>>=
library(ggplot2)
res = read.csv("pred_coefs.csv")
res$y = factor(res$y, levels=c(">30% videos", ">50% videos", ">80% videos", ">60% pctile grade", ">30% assessments", ">50% assessments", ">80% assessments", ">80% pctile grade"))
res$y = factor(res$y, labels=c("> 30% videos", "> 50% videos", "> 80% videos", "> 60th percentile grade", "> 30% assessments", "> 50% assessments", "> 80% assessments", "> 80th percentile grade"))
res$coef2 = factor(res$coef2, levels=rev(c("Intercept", "Gender:F", "Age (norm.)", "Educ.:Bachelor+", "Prior Exp.", "Intent:All", "Hours:2-4", "Hours:4+ ", "Prior MOOCs:1-3", "Prior MOOCs:4+ ", "Geo:Europe", "Geo:Oceania", "Geo:Africa", "Geo:Asia", "Geo:S.America")))
ggplot(subset(res, coef2!="Intercept"), 
       aes(coef2, 100*est, ymin=100*(est-1.96*se), ymax=100*(est+1.96*se), color=factor(sign))) + 
  geom_hline(xintercept=0) + geom_pointrange() + facet_wrap(~y, ncol=4) + coord_flip() + 
  theme_minimal() + theme(legend.position="none",axis.title=element_text(vjust=0)) + 
  scale_color_manual(values=c('red','grey30','green3')) +
  labs(y="Predicted change in probability of achieving each `milestone` (95% CIs)", x="")
@

>>>>

<<s1coefs, echo=FALSE, fig.env='figure*', fig.pos='ht', fig.height=6, fig.width=10, fig.cap='Coefficients of predictors (binary, except for normalized age) from logistic mixed-effects model predicting persistence and performance milestones (prop. videos watched, prop. assessments completed, and grade percentile). The baseline group were male learners in North America of average age who had not earned a bachelor\'s degree, without prior experience in the topic or other MOOCs, not intending to complete the course, and prepared to spend under two hours per week on it. An estimate of -20 indicates a 20\\% points lower probability of achieving a milestone.'>>=
library(ggplot2)
res = read.csv("pred_coefs.csv")
res$y = factor(res$y, levels=c(">30% videos", ">50% videos", ">80% videos", ">60% pctile grade", ">30% assessments", ">50% assessments", ">80% assessments", ">80% pctile grade"))
res$y = factor(res$y, labels=c("> 30% videos", "> 50% videos", "> 80% videos", "> 60th percentile grade", "> 30% assessments", "> 50% assessments", "> 80% assessments", "> 80th percentile grade"))
res$coef2 = factor(res$coef2, levels=rev(c("Intercept", "Gender:F", "Age (norm.)", "Educ.:Bachelor+", "Prior Exp.", "Intent:All", "Hours:2-4", "Hours:4+ ", "Prior MOOCs:1-3", "Prior MOOCs:4+ ", "Geo:Europe", "Geo:Oceania", "Geo:Africa", "Geo:Asia", "Geo:S.America")))

# This is what we submitted
ggplot(subset(res, coef2!="Intercept"), 
       aes(coef2, 100*est, ymin=100*(est-1.96*se), ymax=100*(est+1.96*se), color=factor(sign))) + 
  geom_hline(xintercept=0) + geom_pointrange() + facet_wrap(~y, ncol=4) + coord_flip() + 
  theme_minimal() + theme(legend.position="none",axis.title=element_text(vjust=0)) + 
  scale_color_manual(values=c('red','grey30','green3')) +
  labs(y="Predicted change in probability of achieving each `milestone` (95% CIs)", x="")

# This is what it should be
# ggplot(subset(res, coef2!="Intercept"), 
#   aes(coef2, 100*(exp(est)-1), ymin=100*(exp(est-1.96*se)-1), ymax=100*(exp(est+1.96*se)-1), color=factor(sign))) + 
#   geom_hline(yintercept=0) + geom_pointrange() + facet_wrap(~y, ncol=4) + coord_flip() + 
#   theme_minimal() + theme(legend.position="none",axis.title=element_text(vjust=0)) + 
#   scale_color_manual(values=c('red','grey30','green3')) +
#   labs(y="Predicted change in probability of achieving each `milestone` (95% CIs)", x="")

@
